Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/table.tex
Change results table

loop1.c & 6 &  & true & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop2.c & 7 &  & true & true & false & false & 1 & 5 & term & 2.5s & 3\\

loop3.c & 8 & true & true & true & true & false & 1 & 5 & term & 2.7s & 3\\

loop4.c & 13 &  & true & true & false & false & 2 & 5 & term & 3.2s & 17\\

loop5.c & 13 &  & true & true & false & false & 2 & 5 & term & 2.9s & 8\\

loop6.c & 6 &  & false & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop7.c & 7 &  & true & unk & false & false & unk & 5 & term & 18.2s & 10\\

loop8.c & 6 &  & true & true & true & true & 1 & 5 & term & 2.4s & 1\\

loop9.c & 11 & true & true & false & false & false & 1 & 5 & term & 3.7s & 3\\

loop10.c & 6 &  & true & true & false & false & 1 & 5 & term & 2.5s & 1\\

loop43.c & 9 &  & true & false & false & false & ? & 5 & term & 3.7s & 4\\

loop44.c & 9 & false & true & false & false & false & ? & 5 & nonterm & 2.7s & 4\\

loop45.c & 15 &  & true & false & false & false & ? & 5 & term & 3.4s & 19\\

loop46.c & 9 &  & true & false & false & false & ? & 5 & term & 2.7s & 4\\

loop47.c & 6 &  & true & false & false & false & ? & 5 & term & 3.7s & 4\\

loop48.c & 7 &  & true & false & false & false & ? & 5 & term & 2.5s & 3\\

svcomp1.c & 17 &  & true & true & false & false & 1 & 5 & term & 2.6s & 5\\

svcomp2.c & 13 &  & false & true & false & false & 1 & 5 & term & 2.6s & 6\\

svcomp3.c & 15 &  & true & true & false & false & unk & 5 & term & 36.8s & 36\\

svcomp4.c & 14 & false & true & unk & true & false & unk & 5 & nonterm & 50.6s & 75\\

svcomp5.c & 18 &  & true & false & true & false & unk & 5 & ? & T/O & 46\\

svcomp7.c & 9 & true & true & true & true & false & 1 & 5 & term & 9.7s & 7\\

svcomp8.c & 9 &  & true & unk & false & false & unk & 5 & ? & T/O & 38\\

svcomp9.c & 12 &  & true & unk & false & false & unk & 5 & term & 2.9s & 11\\

svcomp10.c & 15 &  & true & true & false & false & 1 & 5 & term & 3.4s & 19\\

svcomp11.c & 16 &  & true & true & false & false & 1 & 5 & term & 5.5s & 27\\

svcomp13.c & 11 &  & true & true & false & false & 1 & 5 & ? & T/O & 31\\

svcomp14.c & 18 &  & true & true & false & false & 1 & 5 & ? & T/O & 69\\

svcomp15.c & 30 &  & true & true & false & false & 1 & 5 & ? & T/O & 30\\

svcomp16.c & 17 &  & true & true & false & false & 1 & 5 & term & 2.5s & 3\\

svcomp17.c & 17 &  & true & true & false & false & 1 & 5 & nonterm & 0.7s & 1\\

svcomp25.c & 12 &  & true & true & false & false & 1 & 5 & nonterm & 0.7s & 1\\

svcomp26.c & 23 &  & true & true & false & false & 1 & 5 & term & 3.0s & 11\\

svcomp27.c & 13 & false & true & true & false & false & 1 & 5 & ? & T/O & 76\\

svcomp28.c & 18 &  & true & true & false & false & 1 & 5 & ? & T/O & 82\\

svcomp29.c & 9 &  & true & true & false & false & 1 & 5 & ? & T/O & 1\\

svcomp37.c & 22 &  & true & true & false & false & 1 & 5 & term & 2.9s & 14\\

svcomp38.c & 16 & true & true & true & false & false & 1 & 5 & nonterm & 1.0s & 1\\

svcomp39.c & 56 &  & true & true & false & false & 1 & 5 & nonterm & 1.0s & 1\\

svcomp42.c & 22 &  & true & true & false & false & 1 & 5 & ? & T/O & 84\\

>>>>

loop1.c & ? & \tick & 0.06s & \tick & 1.3s & 1\\

loop2.c & ? & \tick & 0.06s & \tick & 1.4s & 4\\

loop3.c & \tick & \tick & 0.06s & \tick & 1.8s & 8\\

loop4.c & ? & \tick & 0.12s & \tick & 2.9s & 18\\

loop5.c & ? & \tick & 0.12s & \tick & 5.3s & 18\\

loop6.c & ? & \tick & 0.05s & \tick & 1.2s & 1\\

loop7.c & ? & \xmark & 0.05s & \tick & 8.3s & 17\\

loop8.c & ? & \xmark & 0.06s & \tick & 1.3s & 1\\

loop9.c & \tick & \tick & 0.11s & \tick & 1.6s & 1\\

loop10.c & ? & \xmark & 0.05s & \tick & 1.3s & 1\\

loop43.c & ? & \tick & 0.07s & \tick & 1.5s & 1\\

loop44.c & \xmark & \xmark & 0.05s & \xmark & 10.5s & 9\\

loop45.c & ? & \tick & 0.12s & \tick & 4.3s & 18\\

loop46.c & ? & \xmark & 0.05s & \tick & 1.5s & 2\\

loop47.c & ? & \tick & 0.10s & \tick & 1.8s & 1\\

loop48.c & ? & \tick & 0.06s & \tick & 1.4s & 4\\

loop49.c & ? & \xmark & 0.05s & ? & T/O & 206\\

svcomp1.c & ? & \tick & 0.11s & \tick & 2.3s & 2\\

svcomp2.c & ? & \tick & 0.05s & \tick & 1.5s & 9\\

svcomp3.c & ? & \tick & 0.15s & \tick & 146.4s & 43\\

svcomp4.c & \xmark & \xmark & 0.09s & \xmark & 2.1s & 7\\

svcomp5.c & ? & \tick & 0.38s & ? & T/O & 46\\

svcomp6.c & ? & ? & T/O & \tick & 29.1s & 28\\

svcomp7.c & \tick & \tick & 0.09s & \tick & 5.5s & 17\\

svcomp8.c & ? & \xmark & 0.05s & ? & T/O & 37\\

svcomp9.c & ? & \tick & 0.10s & \tick & 1.5s & 8\\

svcomp10.c & ? & \tick & 0.11s & \tick & 4.5s & 18\\

svcomp11.c & ? & \tick & 0.20s & \tick & 14.6s & 33\\

svcomp12.c & ? & ? & T/O & \tick & 10.9s & 24\\

svcomp13.c & ? & \xmark & 0.07s & \tick & 35.1s & 62\\

svcomp14.c & ? & ? & T/O & \tick & 30.8s & 26\\

svcomp15.c & ? & \xmark & 0.12s & ? & T/O & 191\\

svcomp16.c & ? & \tick & 0.06s & \tick & 2.2s & 3\\

svcomp17.c & ? & \tick & 0.05s & ? & T/O & 32\\

svcomp18.c & ? & \xmark & 0.27s & ? & T/O & 26\\

svcomp25.c & ? & \xmark & 0.05s & ? & T/O & 26\\

svcomp26.c & ? & \tick & 0.26s & \tick & 3.2s & 23\\

svcomp27.c & \xmark & \tick & 0.11s & ? & T/O & 67\\

svcomp28.c & ? & \tick & 0.13s & ? & T/O & 79\\

svcomp29.c & ? & \xmark & 0.05s & ? & T/O & 1\\

svcomp37.c & ? & \tick & 0.16s & \tick & 2.1s & 10\\

svcomp38.c & \tick & \tick & 0.10s & ? & T/O & 1\\

svcomp39.c & ? & \tick & 0.25s & ? & T/O & 1\\

svcomp40.c & ? & \xmark & 0.07s & ? & T/O & 30\\

svcomp41.c & ? & \xmark & 0.07s & ? & T/O & 27\\

svcomp42.c & ? & \tick & 0.22s & ? & T/O & 85\\
